Structuring College Access

### 2025-03-01 index.qmd
ugh. AIAN loop messed

writeLines("## AI/AN students")

@@

    # If this is the 1st slide => show in TOC (no .hide).
    # Otherwise => hide from TOC with {.hide}.
    if (i == 1) {
      writeLines(str_c("### ", heading_text))
    } else {
      writeLines(str_c("### ", heading_text, " {.hide}"))
    }

@@

    # Call your helper function; it prints "#### <title from _title.txt>"
    # and displays the figure + footnotes.
    insert_figure(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type_native
    )
  }
}

>>>>

# Make AI/AN a top-level heading (level 1)
writeLines("# AI/AN students")

@@

    # If this is the 1st slide => show in TOC (no .hide).
    # Otherwise => hide from TOC with {.hide}.
    if (i == 1) {
      writeLines(str_c("## ", heading_text))
    } else {
      writeLines(str_c("## ", heading_text, " {.hide}"))
    }

@@

    # Call your helper function; it prints a heading/caption
    # and displays the figure + footnotes.
    insert_figure(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type_native
    )
  }
}
